Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-15 shanghai.tex
Still working on Part 2.
Moving to a different computer.

\begin{theorem}\label{thm:application}
Let $d$ be a positive integer.
\begin{enumerate}
\item 
For every algebraic torus $T$ over $K$, the trace of Frobenius 
  \[
\trFrob{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
  \]
is an isomomorphism. 
\item The isomorphism $\trFrob{T,d}$ is functorial in the following sense: $T \mapsto \trFrob{T,d}$ is a natural transformation
from the additive functor
\[T \mapsto \QCiso{\GN{T}_d}\]
to the additive functor
\[
T \mapsto \Hom_{<d}(T(K),\EEx).
\]
\item
For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
\[
\begin{tikzcd}
\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
\end{tikzcd}
\]
\end{enumerate}
\end{theorem}

Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.  If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.  Then there is a canonical isomorphism
\[
\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
\]
The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
\[
\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
\]
and thus a functor on character sheaves through pullback.

@@

  Next we show that this isomorphism is functorial.
The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$. When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.

  Finally, we turn to restriction of scalars.
\end{proof}

>>>>

\begin{theorem}\label{thm:application}
Let $d$ be a positive integer.
\begin{enumerate}
\item 
For every algebraic torus $T$ over $K$, the trace of Frobenius 
  \[
\trFrob{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
  \]
is an isomomorphism. 
\item The isomorphism $\trFrob{T,d}$ is functorial in the following sense: $T \mapsto \trFrob{T,d}$ is a natural transformation
from the additive functor
\[T \mapsto \QCiso{\GN{T}_d}\]
to the additive functor
\[
T \mapsto \Hom_{<d}(T(K),\EEx).
\]
\end{enumerate}
\end{theorem}

@@

  Next we show that this isomorphism is functorial.
The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$. When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
\end{proof}

For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
\[
\begin{tikzcd}
\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
\end{tikzcd}
\]
Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.  If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.  Then there is a canonical isomorphism
\[
\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
\]
The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
\[
\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
\]
and thus a functor on character sheaves through pullback.
